Confirmation of Wide-Field Signatures in Redshifted 21~cm Power Spectra using Murchison Widefield Array Observations

### 2015-04-01 ms.tex
Modify abstract
From ed26e72:
============

In ms.tex,

(*) Add a sentence at the beginning of the Abstract
Add more emphasis in the Abstract
From 097d9e5:
============

In ms.tex,

(*) Add emphasis on critical input for HERA and SKA in the Abstract

While probing H~{\sc i} in the epoch of reionization (EoR) through modeling of delay spectra of measurements between antenna pairs, it has recently emerged that the foreground structure, the nature of wide-field measurements and the antenna aperture imprint a characteristic {\it pitchfork}-shaped signature. This feature is characterized by enhanced power from foreground emission in Fourier modes mapped to regions near the horizon, and is significant for EoR studies because Fourier modes considered to be most sensitive for the cosmological H~{\sc i} signal are very susceptible to contamination from these regions. By improving MWA data sensitivity through coherent averaging of 12 independent snapshots aligned in local sidereal time across different observing nights, we provide the first confirmation of the prediction with a signal-noise ratio $>10$.

% Foreground emission is currently the primary limitation to detection of redshifted H~{\sc i} emission from the epoch of reionization. Modern radio telescopes that target this cosmological signal are typically wide-field instruments. Through modeling of delay spectra measured between antenna pairs, it has recently emerged that wide-field measurements imprint a characteristic {\it pitchfork}-shaped signature in this Fourier domain. This predicted feature is characterized by enhanced power from foreground emission mapped to regions near the horizon and plays a significant role in determining the contamination of the cosmological H~{\sc i} signal. With MWA data sensitivity improved by coherently averaging 12 independent snapshots aligned in local sidereal time across different observing nights, we confirm the prediction with a signal-noise ratio $>10$.

% Foreground emission is currently the primary limitation to detection of redshifted H~{\sc i} emission from the epoch of reionization. Modern radio telescopes that target this cosmological signal are typically wide-field instruments. Through modeling of delay spectra measured between antenna pairs, it has recently emerged that wide-field measurements imprint a characteristic {\it pitchfork}-shaped signature in this Fourier domain. This predicted feature is characterized by enhanced power from foreground emission mapped to regions near the horizon and plays a significant role in determining the contamination of the cosmological H~{\sc i} signal. With MWA data sensitivity improved by coherently averaging 12 independent snapshots aligned in local sidereal time across different observing nights, we confirm the prediction with a signal-noise ratio $>10$.

>>>>

This analysis confirms recent predictions of certain key signatures in the delay spectra of wide-field radio interferometer measurements. While probing H~{\sc i} in the epoch of reionization (EoR) through modeling of delay spectra of measurements between antenna pairs, it has recently emerged that the foreground structure, the nature of wide-field measurements and the antenna aperture imprint a characteristic {\it pitchfork}-shaped signature. This feature is characterized by enhanced power from foreground emission in Fourier modes mapped to regions near the horizon, and is significant for EoR studies because Fourier modes considered to be most sensitive for the cosmological H~{\sc i} signal are very susceptible to contamination from these regions. Thus it forms a critical input to design and analysis choices of future instruments such as the Hydrogen Epoch of Reionization Array and the Square Kilometre Array. By improving Murchison Widefield Array data sensitivity through coherent averaging of 12 independent snapshots aligned in local sidereal time across different observing nights, we provide the first confirmation of the prediction with a signal-noise ratio $>10$.
